\documentclass[10pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\usepackage{blindtext}
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{tikz}
\usetikzlibrary{arrows,automata,shadows,positioning,shapes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{cancel}
\usepackage{amsthm}
\usepackage{epstopdf}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{subfiles}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{wrapfig}

\begin{document}
  \section*{Exercise 3}
    \subsection*{a)}
      \begin{displaymath}
        \begin{array}{l c l}
          X_{i}(f) & : & \text{Input signal} \\
          Y_{i}(f) & : & \text{Electric signal for loudspeaker} \\
          L(f),R(f)& : & \text{Acoustic signal produced by loudspeaker} \\
          Z_{i}(f) & : & \text{Signal arriving at the ear} \\
          O_{xx}   & : & \text{head related transfer function}
        \end{array}
      \end{displaymath}

      Goal: Find $Y_{i}(f)$ such that $Z_{i}(f)\overset{!}{=} X_{i}(f)$.

      At each ear a acoustic signal of each loudspeaker arrives. The signal
      arriving from each loudspeaker is of the form $Y_{L}\cdot L\cdot
      O_{uL}$ for each ear $u$ and the left loudspeaker, analogous for the right
      loudspeaker. Because the frequencies of
      the two loudspeaker (left and right) the signal arriving at the ear is the
      sum of signal of each loudspeaker. So $Z_{i}$ is the following.
      \begin{displaymath}
        Z_{L}=Y_{R}\cdot L\cdot O_{LL} + Y_{L}\cdot R\cdot O_{LR}
      \end{displaymath}
      The formula for $Z_{R}$ is analogous. With both $Z_{R}$ and $Z_{L}$ 

      \begin{eqnarray}
          Y_{R}&=&\frac{Z_{R}-Y_{L} L\cdot O_{RL}}{R\cdot O_{RR}} \\
          Y_{L}&=&\frac{Z_{L}-Y_{R} R\cdot O_{LR}}{L\cdot O_{LL}} \\
           &=&
            \frac{Z_{L}}{L\cdot O_{LL}} - \frac{Z_{R}-Y_{L} L\cdot
            O_{RL}}{\cancel{R} \cdot O_{RR}} \frac{\cancel{R}\cdot O_{LR}}{L\cdot O_{LL}} \\
           &=&
            \frac{Z_{L}}{L\cdot O_{LL}}-
            \frac{Z_{R}O_{LR}}{L\cdot O_{RR} O_{LL}}+
            \frac{Y_{L} \cancel{L}\cdot O_{RL}O_{LR}}{\cancel{L}\cdot
            O_{RR}O_{LL}} \\
          Y_{L}\left( 1-\frac{O_{LR}O_{RL}}{O_{RR}O_{LL}} \right) &=&
          L^{-1}\left( \frac{Z_{L}}{O_{LL}} -\frac{Z_{R}O_{LR}}{O_{RR}O_{LL}}\right) \\
          Y_{L}&=&
          L^{-1}\left( \frac{Z_{L}}{O_{LL}} -\frac{Z_{R}O_{LR}}{O_{RR}O_{LL}}\right)
            \left( 1-\frac{O_{LR}O_{RL}}{O_{RR}O_{LL}} \right)^{-1} \\
          &=&
            L^{-1}\left( \frac{Z_{L}}{O_{LL}}
            \left(\frac{1}{1-\frac{O_{LR}O_{RL}}{O_{LL}O_{RR}}}\right)
            -\frac{Z_{R}O_{LR}}{O_{RR}O_{LL}} 
            \left(\frac{1}{1-\frac{O_{LR}O_{RL}}{O_{LL}O_{RR}}}\right)
            \right) \\
          &=&
            L^{-1}\left(
            \frac{Z_{L}}{O_{LL}-\frac{O_{LR}O_{RL}}{\cancel{O_{LL}}O_{RR}}\cancel{O_{LL}}}
            -\frac{Z_{R}O_{LR}}{O_{LL}O_{RR}-\frac{O_{RL}O_{LR}}{O_{LL}
            \cancel{O_{RR}}}\cancel{O_{RR}}}
            \right) \\
          &=& L^{-1} \left(
            \frac{O_{RR}}{O_{RR}O_{LL}-O_{LR}O_{RL}}Z_{L}
            -\frac{O_{LR}}{O_{LL}}\frac{O_{LL}}{O_{LL}O_{RR}-O_{RL}O_{LR}}Z_{R}
          \right)
      \end{eqnarray}

    \subsection*{b)}
      The equation can be split into two parts. The part for the right ear and
      the part for the left ear. Because the sound you can hear with your right
      ear from the left loudspeaker should be reduced, the part for the left ear
      has a negative sign. Because the frequencies are manipulated during the
      time between loudspeaker and ear, the made sound is not equal to the sound
      the ear hears. In order to reverse the manipulation the fractions of
      considering $O$ are inserted.
      

    \subsection*{c)}
      The analytical solution is not applicable in praxis because it is
      numerical instable for rather low low frequencies with $O_{LL}\sim O_{LR}$
      and $O_{RR}\sim O_{RL}$. This leads to a denominator close to $0$.


\end{document}

